Risk Perceptions for Wearable Devices

### 2015-03-05 tex-inputs/abstract.tex
Major editing of abstract.

\begin{abstract}
Along with great benefits, wearable devices, or ``wearables,'' bring new potential privacy and security risks which expose users' activities without their awareness or consent. With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture, but human attention is a finite resource. Therefore, user concerns should be investigated to warn users only about situations they are likely to care about. Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoiding scandalous breaches of privacy. To this end, we conducted the first large-scale study to investigate user security and privacy concerns for wearable devices. We surveyed 1,784 Internet users for their perceptions of wearable devices and contribute: relevant perceived risks for wearables, effects of data type and data recipient on perceived risk, users' self reported concerns, and an assessment of how wearable device capabilities compare to familiar technologies. We conclude with a discussion on future research directions for wearable devices. 
\end{abstract}

>>>>

\begin{abstract}
Wearable devices bring great benefits but also new potential privacy and security risks that could expose users' activities without their awareness or consent.
Effective design of notifications and security controls for wearable devices will require careful attention to prevent habituation and treat user as a scarce resource, which requires understanding which risks have the potential to be most concerning to users.
In this paper, we conduct a large-scale survey to investigate user security and privacy concerns regarding wearable devices. We surveyed 1,784 Internet users for their perceptions of wearable devices and identify risks that are particularly concerning to users, measure the effect of data type and data recipient on perceived risk, study users' self-reported concerns, and compare wearable device risks to those of more familiar technologies.
We hope that this work will inform design of future privacy and security controls for wearable devices.
\end{abstract}
